Similar Article Detection Using Locality Sensitive Hashing Technique on Wikipedia\titlenote{This effort is part of the CMSC828G, Data Intensive Computing with MapReduce, class project.}

### 2013-05-08 article/sigproc-sp.tex
Updated psedocode for algorithm

\documentclass{acm_proc_article-sp}
\usepackage{url}

@@

In this section, we introduce the algorithm that utilizes the locality sensitive hashing.

@@

\begin{table}
MapReduce pseudocode:
\begin{verbatim}
initialize(){
 # configure and set up algorithm parameters
 # F = hash family;
 # L = shingle length;
 # K = vector length;
 # N = number of signatures to emit;
}

map(docid d, wikipage p){
  int sentence ct = 0;
  while s = nextSentence(p){
    shingles = shingleSet(s,L);
    minhashes = new List(|F|);
    for i = 1 ... |F|:
      minhashes[i] = Infinity;
    for g in shingles:
      for i = 1 ... |F|:
        minhashes[i] = min(F_i(g),minhashes[i]);
    for i = 1 ... N:
      sig = select(K, minhahses);
      emit(sig,(docid,sentencect));
    sentencect++;
  }
}
\end{verbatim}

\begin{verbatim}
reduce(signature sig, sentenceids [(d1,s1),(d2,s2) ...]){
  if [[(d1,s1),(d2,s2) ... ]| > 1:
    emit(sig, [(d1,s1), (d2,s2), ...]);
}
\end{verbatim}
\end{table}

>>>>

\documentclass{acm_proc_article-sp}
\usepackage{url}
\usepackage{algpseudocode}

@@

@@

\begin{table}
Minhash MapReduce pseudocode:
\begin{algorithmic}
\Function{initialize}{}
%\Comment{configure and set up algorithm parameters}
 \State $F \gets $ hash family;
 \State $L \gets $ shingle length;
 \State $K \gets $ vector length;
 \State $N \gets $ number of signatures to emit;
\EndFunction

\Function{map}{docid $d$, wikipage $p$}
 \State sentencect $\gets 0$
 %\Comment {Break up article text into sentence}
 \While{$s \gets$ nextSentence($p$)}
  %\Comment{Break up sentence into shingles}
  \State shingles $\gets$ shingleSet($s$,$L$);
  \State minhashes = new List(|F|);
   \For{$i \gets 1 \ldots |F|$}
    \State minhashes[$i$] $\gets \infty$;
   \EndFor
   %\Comment{Calculate set of minhash signature for each sentence}
   \For{$g \in$ shingles}
    \For{$i \gets 1 \ldots |F|$}
     \State minhashes[$i$] $\gets$ min($F_i(g)$,minhashes[$i$]);
    \EndFor
   \EndFor
   %\Comment{Emit $N$ $K$-length signatures}
  \For{$i \gets 1 \ldots N$}
   \State sig = select($K$, minhahses);
   \State emit(sig,(docid,sentencect));
  \EndFor
  \State  sentencect++;
 \EndWhile
\EndFunction
\end{algorithmic}

\begin{algorithmic}
\Function{reduce}{signature sig, sentenceids $S$}
\If{$|S| > 1$}
\State    emit(sig, $S$);
\EndIf
\EndFunction
\end{algorithmic}
\end{table}
